Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-18 ieee_paper.tex
description of CPU case

>>>>

To put things in perspective, we conducted some experiments on a
classical CPU architecture with 2 Intel Core i7 processor, each has 8
cores which support AVX instructions. Both the compiler generated and
the manually written vectorization using AVX instruction reach a
(read) bandwidth of 70GB/s. This indicates that the performance of the
classical SpMV can not overcome 16.8Gflop/s. A generic implementation
of the multiplication of 4 vectors with 4 matrices on the {\tt RBF}
matrix reaches a performance of 27 Gflop/s; while a manual
implementation using AVX instruction reaches a performance of 42
Gflop/s. This confirms that our method is sound and generalizes to
other architecture than the Intel MIC architecture.
